Supplementary Figures and Tables

### 2020-11-13 Supplementary_fig_tab.Rmd
resize fig S12

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.width=5, fig.height=5, fig.show='hold', fig.cap = "Log2 transformed expression level of miR-30a-5p in tumor and normal tissue samples of 87 patients."}

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.width=4, fig.height=4, fig.show='hold', fig.cap = "Log2 transformed expression level of miR-30a-5p in tumor and normal tissue samples of 87 patients."}
